\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2016-04-20 latex/UMEM_CoSim.tex
Added a commenting format for reviewing the paper
Clayton writes in red.
Jerome in blue
Daren in green

\theoremstyle{remark}
\newtheorem{remark}{Remark}

@@

\section{Introduction}

@@

\begin{figure}
\centering
\includegraphics[scale=0.7]{figures/UMEM_overview_new}
\caption{EnergyPlus and CitySim coupling are part of the wider context. Each block in the diagram represents an environment, with the tool/engine name in italics (adapted from \citep{Dorer:2013vt})}
\label{fig:UMEM}
\end{figure}

@@

Variables sent to CitySim by EnergyPlus at each timestep include several variables related to the calculation of heating and cooling loads of a targeted building. These variables are transferred due to the ability of EnergyPlus to model more detailed building systems, schedules, ventilation and internal load types than CitySim. For example, EnergyPlus is flexible enough to model a detailed, radiant heating and cooling system that would be impossible in CiytSim \cite{barbara:2015tz}. EnergyPlus is an engine optimized on the accuracy of building-scale systems, thus CitySim can take advantage of these models through coupling and co-simulation. EnergyPlus sends the heating and cooling loads, the surface temperatures of the exterior surfaces and the ventilation flow rates to CitySim.

@@

INSERT VISTRAILS GRAPHIC HERE

@@

\section{Implementation}\label{Implementation}
The co-simulation process is implemented on two case studies in Switzerland. The first is the ETH Z\"urich Hoenggerberg campus in Z\"urich, Switzerland. The focus of this case study is to compare the impact of the information exchange through co-simulation within the EnergyPlus engine. The intent on this campus was to develop techniques for retrofit analysis using EnergyPlus. The targeted building on this campus is the HPI Building. Raw measured data is available for many of the buildings on campus, thus a simplified calibration procedure is used to reconcile the simulation results.\\

@@

After calibration, a comparison of co-simulation and solo EnergyPlus simulations is made. For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus. A 20.2\% decrease in predicted cooling energy is observed as seen in Figure \ref{fig:hpi_energypluscooling}.

@@

Figure \ref{fig:hpi_energyplusheating} illustates the difference in predicted heating energy consumption across the test year. A consistent offset exists across the time frame of days in January, the peak of the heating season. A more varied discrepancy across the heating months is noticed resulting and overall increase of heating prediction of 4.8\% due to co-simulation.

@@

\subsection{Model development}
The information required in the simulation mainly comprises three parts: physical, geometrical and operational data. The geometry information including the building’s shape, dimension, structure and materials was obtained from the Real Estate and Infrastructure Department of École Polytechnique Fédérale de Lausanne (EPFL), which was responsible for carrying out the project from call to tender to construction. However, since the documents provided were full of details but also conflicting with what has been installed as compared to the documents before construction, the task to realise a precise model of the buildings itself is rather tedious. Besides, it is even more challenging to get the operational data (daily occupancy, lighting and electrical equipment usage level and ventilation rate) as the building has only recently been set in operation mode and as engineers and technicians have been working on improving the controls. Therefore, due to unreliable monitoring data, the calibration step of the model has been unfortunately abandoned.\\

Considering the lack of detailed information about the building, a so-called detailed reference case was modeled with EnergyPlus \citep{Mauree:2015} in which regulation standards applied in the design phase from the SIA norms were used to complete the missing information. A rendering of this model is seen in Figure \ref{fig:model_yang}.

@@

Both the CitySim and EnergyPlus engines are utilized in this case study. The first comparison to observe are the differences between the two engines when focused on the Quartier Nord building.

@@

When simulated in isolation, the CitySim engine predicts a 28.8\% higher heating load than EnergyPlus with the model inputs aligned as closely as possible. Use of the co-simulation, brings the engines to within 5.4\%. Figure \ref{fig:qn_eplusvscitysim_heating} illustrates these differences.

@@

When focusing on solely on EnergyPlus, a 7.5\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_cooling}.

@@

A 2.8\% increase in heating energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_heating}.

@@

\subsection{CitySim co-simulation results}

When focusing on solely on CitySim, a X\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}.

@@

A 30.8\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_heating}.

@@

\section{Conclusion}
The ability to couple and leverage the best aspects of multiple simulation engines can enhance the modeling of large scale urban agglomerations. This paper has outlined one such scenario in which the building-focused EnergyPlus simulation engine is coupled and co-simulated with the urban-scale CitySim engine. This process is implemented through a fully automated work flow process that extract geometry information at the urban-scale, creates the necessary input information, executes each engine with information exchange at each timestep of targeted variables, and accumulates the results for analysis. The process has been implemented on simpflied theoretical scenarios in the past and the key innovation with this work is in implementation on actual case study campuses and targeted buildings. More reliable results of the magnitude of differences between the simulation techniques can be extracted from this scenario.

>>>>

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newcommand{\noteCM}[1]{\footnote{\textcolor{red}{#1}}}
\newcommand{\noteJK}[1]{\footnote{\textcolor{blue}{#1}}}
\newcommand{\noteDT}[1]{\footnote{\textcolor{green}{#1}}}

@@

\section{Introduction}\noteCM{Clayton's notes are red!}\noteJK{Jerome's notes are blue!}\noteDT{Daren's notes are green!}

@@

\begin{figure}
\centering
\includegraphics[scale=0.7]{figures/UMEM_overview_new}
\caption{EnergyPlus and CitySim coupling are part of the wider context. Each block in the diagram represents an environment, with the tool/engine name in italics (\citep{thomas2014multiscale}, adapted from \citep{Dorer:2013vt})}
\label{fig:UMEM}
\end{figure}

@@

Variables sent to CitySim by EnergyPlus at each time step include several variables related to the calculation of heating and cooling loads of a targeted building. These variables are transferred due to the ability of EnergyPlus to model more detailed building systems, schedules, ventilation and internal load types than CitySim. For example, EnergyPlus is flexible enough to model a detailed, radiant heating and cooling system that would be impossible in CiytSim \cite{barbara:2015tz}. EnergyPlus is an engine optimized on the accuracy of building-scale systems, thus CitySim can take advantage of these models through coupling and co-simulation. EnergyPlus sends the heating and cooling loads, the surface temperatures of the exterior surfaces and the ventilation flow rates to CitySim.

@@

INSERT VISTRAILS GRAPHIC HERE\noteCM{Daren -- can you give me a good screenshot of the Vistrails for the HPI building? Pretty please.}

@@

\section{Implementation}\label{Implementation and results}
The co-simulation process is implemented on two case studies in Switzerland. The first is the ETH Z\"urich Hoenggerberg campus in Z\"urich, Switzerland. The focus of this case study is to compare the impact of the information exchange through co-simulation within the EnergyPlus engine. The intent on this campus was to develop techniques for retrofit analysis using EnergyPlus. The targeted building on this campus is the HPI Building. Raw measured data is available for many of the buildings on campus, thus a simplified calibration procedure is used to reconcile the simulation results.\\

@@

After calibration, a comparison of co-simulation and solo EnergyPlus simulations is made. For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus. A 20.2\% decrease in predicted cooling energy is observed as seen in Figure \ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating} illustrates the difference in predicted heating energy consumption across the test year. A consistent offset exists across the time frame of days in January, the peak of the heating season. A more varied discrepancy across the heating months is noticed resulting and overall increase of heating prediction of 4.8\% due to co-simulation. The exchange of long wave radiation for this particular site is likely greater due to the proximity of surrounding buildings. These performance differences due to co-simulation are compared to a theoretical single-zone case study in which there was a 15-30\% increase in heating energy and a 4-11\% decrease in cooling energy. The results form this scenario are less extreme from the heating side and more extreme from the cooling side.

@@

@@

\subsection{Model development}
The information required in the simulation mainly comprises three parts: physical, geometrical and operational data. The geometry information including the shape, dimension, structure and materials was obtained from the Real Estate and Infrastructure Department of École Polytechnique Fédérale de Lausanne (EPFL), which was responsible for carrying out the project from call to tender to construction. However, since the documents provided were full of details but also conflicting with what has been installed as compared to the documents before construction, the task to realise a precise model of the buildings itself is rather tedious. Besides, it is even more challenging to get the operational data (daily occupancy, lighting and electrical equipment usage level and ventilation rate) as the building has only recently been set in operation mode and as engineers and technicians have been working on improving the controls. Therefore, due to unreliable monitoring data, the calibration step of the model has been unfortunately abandoned.\\

Considering the lack of detailed information about the building, a so-called detailed reference case was modeled with EnergyPlus \citep{Mauree:2015to} in which regulation standards applied in the design phase from the SIA norms were used to complete the missing information. A rendering of this model is seen in Figure \ref{fig:model_yang}.

@@

Both the CitySim and EnergyPlus engines are utilized in this case study. The first comparison to observe are the differences between the two engines when focused on the Quartier Nord building. When simulated in isolation, the CitySim engine predicts a 28.6\% increase in heating load and a 44.4\% increase in cooling load than EnergyPlus with the model inputs aligned as closely as possible. This phenomenon is due to the differences in the way each of these engines calculates heating and cooling loads. Use of the co-simulation process, brings the engines to within 5.4\%. Figure \ref{fig:qn_eplusvscitysim_heating} illustrates these differences.

@@

@@

When focusing on solely on EnergyPlus, a 7.5\% decrease in cooling energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_cooling}. A 2.8\% increase in heating energy is observed, as seen in Figure \ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less

@@

@@

\subsection{CitySim co-simulation results}\noteCM{Jerome -- I really need some help interpreting this...}

When focusing on solely on CitySim, a 26.9\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}. A 49.1\% decrease in heating energy is observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_heating}.

@@

@@

\section{Conclusion}
The ability to couple and leverage the best aspects of multiple simulation engines can enhance the modeling of large scale urban agglomerations. This paper has outlined two such scenarios in which the building-focused EnergyPlus simulation engine is coupled and co-simulated with the urban-scale CitySim engine. This process is implemented through a fully automated work flow process that extract geometry information at the urban-scale, creates the necessary input information, executes each engine with information exchange at each timestep of targeted variables, and accumulates the results for analysis. The process has been implemented on simplified theoretical scenarios in the past and the key innovation with this work is in implementation on actual case study campuses and targeted buildings. The results illustrate that the differences between the co-simulation and solo environments are within range of previous theoretical models. More reliable results of the magnitude of differences between the simulation techniques can be extracted from these real-world scenarios.
